\vspace{1.0cm} \LARGE \bf Reassortment between influenza B lineages and the emergence of a co-adapted PB1-PB2-HA gene complex

### 2014-02-24 fluB.tex
Add my funding.
Also altering GISAID's reference.
Uncomment some future "figure supplements".
I figure if the aSPR figure gets supplements, so should the deltaTMRCA
figure (both show normalised values), especially since the dTMRCA
supplements show something very dramatic and explains what's going on a
bit better.

%\begin{figure}
%\centering  
%\includegraphics[width=0.65\textwidth]  {supp_figures/InfB_supp_deltaTMRCA_trees.png}
%\caption{\textbf{Mean $\dtmrca$ between all pairs of trees of segments.}}
%\label{deltaTMRCAtrees}
%\end{figure}

%\begin{figure}
%\centering  
%\includegraphics[width=0.65\textwidth]  {supp_figures/InfB_supp_deltaTMRCA_replicates.png}
%\caption{\textbf{Mean $\dtmrca$ between replicate trees of each segment.}}
%\label{deltaTMRCAreplicates}
%\end{figure}

@@

\section*{Acknowledgements}
GD was supported by a NERC studentship..... 
TB was supported by a Newton International Fellowship from the Royal Society. 
The research leading to these results has received funding from the European Research Council under the European Community's Seventh Framework Programme (FP7/2007-2013) under Grant Agreement no. 278433-PREDEMICS and ERC Grant agreement no. 260864.
AR and SL acknowledge the support of the Wellcome Trust (grant no. 092807).

>>>>

\begin{figure}
\centering  
\includegraphics[width=0.65\textwidth]  {supp_figures/InfB_supp_deltaTMRCA_trees.png}
\caption{\textbf{Mean $\dtmrca$ between all pairs of trees of segments.}}
\label{deltaTMRCAtrees}
\end{figure}

\begin{figure}
\centering  
\includegraphics[width=0.65\textwidth]  {supp_figures/InfB_supp_deltaTMRCA_replicates.png}
\caption{\textbf{Mean $\dtmrca$ between replicate trees of each segment.}}
\label{deltaTMRCAreplicates}
\end{figure}

@@

\section*{Acknowledgements}
GD was supported by a NERC studentship D76739X.
TB was supported by a Newton International Fellowship from the Royal Society. 
The research leading to these results has received funding from the European Research Council under the European Community's Seventh Framework Programme (FP7/2007-2013) under Grant Agreement no. 278433-PREDEMICS and ERC Grant agreement no. 260864.
AR and SL acknowledge the support of the Wellcome Trust (grant no. 092807).
